\documentclass[12pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{xltabular}
\usepackage{array}
\usepackage{lmodern}
\usepackage{ragged2e}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\renewcommand{\arraystretch}{1.12}

\newcolumntype{L}[1]{>{\RaggedRight\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\Centering\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}

\begin{document}

\section*{Remaining PFE Sprint Backlog Report}

\footnotesize

\begin{xltabular}{\textwidth}{|L{2.2cm}|L{3.0cm}|L{2.4cm}|Y|}
\caption{Remaining PFE Timeline After Sprint 0} \\ \hline
\textbf{Sprint} & \textbf{Duration} & \textbf{Cumulative} & \textbf{Main Goal} \\ \hline
Sprint 1 & 25 days (3.5 weeks) & Day 1 to Day 25 & HR authentication, taxonomy (Skills/Departments CRUD), job posting management, cascade deletion, and admin shell layout. \\ \hline
Sprint 2 & 27 days (4 weeks) & Day 26 to Day 52 & Public candidate application flow (submit, track, delete) and HR review operations. \\ \hline
Sprint 3 & 26 days (3.5 weeks) & Day 53 to Day 78 & AI processing pipeline (parsing, scoring, standardized CV), CV templates, and PDF generation. \\ \hline
Sprint 4 & 24 days (3.5 weeks) & Day 79 to Day 102 & Decision support (filtering, bulk actions), analytics dashboard, AI evaluation config, recommendations, and chatbot. \\ \hline
\textbf{Total remaining} & \textbf{102 calendar days} &  & \textbf{3 members working in parallel} \\ \hline
\end{xltabular}

\vspace{6pt}
\begin{xltabular}{\textwidth}{|L{2.4cm}|C{1.0cm}|C{1.0cm}|C{1.0cm}|C{1.0cm}|C{1.2cm}|Y|}
\caption{Workload Distribution Summary (days per member)} \\ \hline
\textbf{Member} & \textbf{S1} & \textbf{S2} & \textbf{S3} & \textbf{S4} & \textbf{Total} & \textbf{Focus Areas} \\ \hline
Oussama & 25 & 27 & 26 & 24 & 102 & Auth setup, job posting CRUD, pipeline orchestration, fit evaluation, filtering, chatbot \\ \hline
Maalek & 25 & 27 & 26 & 24 & 102 & Skill CRUD, admin shell, resume extraction, CV generation, analytics, recommendations \\ \hline
Lina & 25 & 27 & 26 & 24 & 102 & Auth UI, departments, job posting forms, CV parsing (Ollama), evaluation config, dashboard \\ \hline
\end{xltabular}

%% ===== SPRINT 1 =====
\subsection*{Sprint 1 Product Backlog}
\begin{xltabular}{\textwidth}{|L{1.2cm}|C{0.5cm}|Y|C{0.7cm}|L{1.5cm}|C{0.7cm}|}
\caption{Sprint 1 Product Backlog (25 days / member)} \\ \hline
\textbf{Story} & \textbf{Part} & \textbf{Product Backlog Item} & \textbf{Dur.} & \textbf{Assigned To} & \textbf{Prio.} \\ \hline
S1-US1 & BE & Strapi Admin authentication configuration and JWT setup. & 4 & Oussama & H \\ \hline
S1-US1 & FE & Login page, auth guard, and token interceptor. & 6 & Lina & H \\ \hline
S1-US2 & BE & Skill content-type, unique constraint, and CRUD routes. & 3 & Maalek & H \\ \hline
S1-US2 & FE & Skills management page (list, create, edit, delete). & 7 & Oussama & H \\ \hline
S1-US3 & BE & Skills search/filter endpoint. & 3 & Lina & M \\ \hline
S1-US3 & FE & Skills autocomplete component in requirements form. & 3 & Maalek & M \\ \hline
S1-US4 & BE & Department content-type, unique constraint, and CRUD routes. & 3 & Oussama & M \\ \hline
S1-US4 & FE & Departments management page (list, create, edit, delete). & 5 & Lina & M \\ \hline
S1-US5 & BE & Departments search/filter endpoint. & 2 & Maalek & L \\ \hline
S1-US5 & FE & Departments autocomplete component in requirements form. & 4 & Oussama & L \\ \hline
S1-US6 & BE & JobPosting content-type with embedded requirements JSON and CRUD routes. & 5 & Maalek & H \\ \hline
S1-US6 & FE & Job posting form UI (create/edit with requirements sub-form). & 8 & Lina & H \\ \hline
S1-US7 & BE & Job posting status transition logic (draft/open/closed). & 4 & Oussama & M \\ \hline
S1-US7 & FE & Status toggle UI and confirmation dialogs. & 3 & Maalek & M \\ \hline
S1-US8 & BE & Cascade deletion logic (candidates + resume files on job delete). & 3 & Lina & L \\ \hline
S1-US8 & FE & Delete confirmation dialog with cascade warning. & 3 & Oussama & L \\ \hline
S1-US9 & FE & Admin shell with sidebar navigation and unified HR portal layout. & 9 & Maalek & H \\ \hline
\textbf{Total} &  & \textbf{Sprint 1: 25 days / member} & \textbf{75} &  &  \\ \hline
\end{xltabular}

%% ===== SPRINT 2 =====
\subsection*{Sprint 2 Product Backlog}
\begin{xltabular}{\textwidth}{|L{1.2cm}|C{0.5cm}|Y|C{0.7cm}|L{1.5cm}|C{0.7cm}|}
\caption{Sprint 2 Product Backlog (27 days / member)} \\ \hline
\textbf{Story} & \textbf{Part} & \textbf{Product Backlog Item} & \textbf{Dur.} & \textbf{Assigned To} & \textbf{Prio.} \\ \hline
S2-US1 & BE & Public route returning only open job postings. & 3 & Oussama & M \\ \hline
S2-US1 & FE & Public job listing page with cards/table. & 6 & Lina & M \\ \hline
S2-US2 & BE & Candidate creation endpoint with resume upload and file validation. & 5 & Maalek & H \\ \hline
S2-US2 & FE & Application form UI with file input and validation feedback. & 7 & Oussama & H \\ \hline
S2-US3 & BE & Consent fields, consentAt timestamp, retentionUntil auto-calculation. & 4 & Lina & H \\ \hline
S2-US3 & FE & Consent checkbox and GDPR notice in application form. & 3 & Maalek & H \\ \hline
S2-US4 & BE & Public token generation and tracking endpoint. & 5 & Oussama & H \\ \hline
S2-US4 & FE & Application tracking page (status display via token). & 4 & Lina & H \\ \hline
S2-US5 & BE & Delete-by-token endpoint (GDPR self-service). & 3 & Maalek & M \\ \hline
S2-US5 & FE & Delete confirmation page for public applicants. & 3 & Oussama & M \\ \hline
S2-US6 & BE & HR candidate listing route with pagination. & 3 & Lina & H \\ \hline
S2-US6 & FE & HR candidate review queue UI (table with sorting). & 8 & Maalek & H \\ \hline
S2-US7 & BE & Candidate detail and resume download endpoint. & 3 & Oussama & M \\ \hline
S2-US7 & FE & Candidate detail view with resume download button. & 6 & Lina & M \\ \hline
S2-US8 & BE & Status update route with allowed transitions. & 3 & Maalek & H \\ \hline
S2-US8 & FE & Status change dropdown/dialog in candidate view. & 6 & Oussama & H \\ \hline
S2-US9 & BE & HR notes field update endpoint. & 4 & Lina & M \\ \hline
S2-US9 & FE & Notes editor component in candidate detail. & 5 & Maalek & M \\ \hline
\textbf{Total} &  & \textbf{Sprint 2: 27 days / member} & \textbf{81} &  &  \\ \hline
\end{xltabular}

%% ===== SPRINT 3 =====
\subsection*{Sprint 3 Product Backlog}
\begin{xltabular}{\textwidth}{|L{1.2cm}|C{0.5cm}|Y|C{0.7cm}|L{1.5cm}|C{0.7cm}|}
\caption{Sprint 3 Product Backlog (26 days / member)} \\ \hline
\textbf{Story} & \textbf{Part} & \textbf{Product Backlog Item} & \textbf{Dur.} & \textbf{Assigned To} & \textbf{Prio.} \\ \hline
S3-US1 & BE & Pipeline orchestration: chain extract → parse → evaluate → generate. & 8 & Oussama & H \\ \hline
S3-US1 & FE & Processing status indicator and error display in candidate view. & 4 & Lina & H \\ \hline
S3-US2 & BE & Resume text extraction from PDF (pdf-parse), DOCX (mammoth), and TXT. & 8 & Maalek & H \\ \hline
S3-US3 & BE & Parse CV via Ollama into structured JSON (contact, skills, experience, education, projects). & 10 & Lina & H \\ \hline
S3-US4 & BE & Deterministic fit evaluation: skills coverage, experience match, completeness scoring. & 10 & Oussama & H \\ \hline
S3-US5 & BE & Generate standardized CV markdown via Ollama with template context. & 8 & Maalek & H \\ \hline
S3-US5 & FE & Standardized CV preview display in candidate detail. & 4 & Lina & H \\ \hline
S3-US6 & BE & CV template catalog data and selection route. & 4 & Oussama & M \\ \hline
S3-US6 & FE & Template picker UI (gallery with preview thumbnails). & 6 & Maalek & M \\ \hline
S3-US7 & BE & Playwright-based HTML-to-PDF conversion endpoint. & 4 & Lina & M \\ \hline
S3-US7 & FE & Download standardized CV button (HR and public token flows). & 4 & Oussama & M \\ \hline
S3-US8 & BE & Reprocess logic: reset status to new and re-trigger pipeline. & 4 & Maalek & M \\ \hline
S3-US8 & FE & Reprocess button with confirmation in candidate detail. & 4 & Lina & M \\ \hline
\textbf{Total} &  & \textbf{Sprint 3: 26 days / member} & \textbf{78} &  &  \\ \hline
\end{xltabular}

%% ===== SPRINT 4 =====
\subsection*{Sprint 4 Product Backlog}
\begin{xltabular}{\textwidth}{|L{1.2cm}|C{0.5cm}|Y|C{0.7cm}|L{1.5cm}|C{0.7cm}|}
\caption{Sprint 4 Product Backlog (24 days / member)} \\ \hline
\textbf{Story} & \textbf{Part} & \textbf{Product Backlog Item} & \textbf{Dur.} & \textbf{Assigned To} & \textbf{Prio.} \\ \hline
S4-US1 & BE & Multi-criteria filter query params (status, score, job, search). & 3 & Lina & H \\ \hline
S4-US1 & FE & Filter bar UI with dropdowns, search input, and chips. & 5 & Oussama & H \\ \hline
S4-US2 & BE & Score-threshold operator/value filtering logic. & 3 & Maalek & M \\ \hline
S4-US2 & FE & Score threshold input with operator selector. & 3 & Lina & M \\ \hline
S4-US3 & BE & Filter-by-job-posting query parameter support. & 3 & Oussama & M \\ \hline
S4-US3 & FE & Job posting dropdown filter in candidate list. & 3 & Maalek & M \\ \hline
S4-US4 & BE & Bulk status update route (array of candidate IDs). & 3 & Lina & H \\ \hline
S4-US4 & FE & Multi-select checkboxes and bulk action toolbar. & 5 & Oussama & H \\ \hline
S4-US5 & BE & Analytics aggregation endpoint (KPIs, distributions, histograms). & 6 & Maalek & H \\ \hline
S4-US5 & FE & Analytics dashboard page with charts (Chart.js/ng2-charts). & 5 & Lina & H \\ \hline
S4-US6 & BE & Meta API route for default CV template setting. & 3 & Oussama & M \\ \hline
S4-US6 & FE & Default template selection UI in settings. & 4 & Maalek & M \\ \hline
S4-US7 & BE & Evaluation config schema and scoring integration per job. & 5 & Lina & M \\ \hline
S4-US7 & FE & Evaluation config form in job posting settings. & 4 & Oussama & M \\ \hline
S4-US8 & BE & Job recommendation engine (skill matching, compatibility ranking). & 8 & Maalek & L \\ \hline
S4-US8 & FE & Recommendations display with compatibility scores. & 3 & Lina & L \\ \hline
S4-US9 & BE & Chat endpoint with Ollama integration and session management. & 4 & Oussama & L \\ \hline
S4-US9 & FE & Chatbot floating widget with message history. & 2 & Lina & L \\ \hline
\textbf{Total} &  & \textbf{Sprint 4: 24 days / member} & \textbf{72} &  &  \\ \hline
\end{xltabular}

\end{document}
