\begin{longtable}{|p{1.4cm}|p{3.2cm}|p{6.3cm}|p{1.7cm}|p{1.2cm}|}
\caption{Sprint 1 Product Backlog Aligned with UML (28 days)} \\ \hline
\textbf{Story} & \textbf{UML Reference} & \textbf{Product Backlog Item} & \textbf{Duration (days)} & \textbf{Priority} \\ \hline
S1-US1 & UC11; User.authenticate() & HR authentication and session flow for protected HR access. & 4 & Must \\ \hline
S1-US2 & UC12; HRUser.addSkill/updateSkill/deleteSkill & Skills taxonomy CRUD (create, update, delete) for reusable requirements. & 4 & Must \\ \hline
S1-US3 & UC12, UC18; HRUser.searchSkills() & Skills search and autocomplete in JobRequirement forms. & 3 & Must \\ \hline
S1-US4 & UC13; HRUser.addDepartment/updateDepartment/deleteDepartment & Departments taxonomy CRUD for organizational classification. & 3 & Must \\ \hline
S1-US5 & UC13, UC19; HRUser.searchDepartments() & Departments search and autocomplete in JobRequirement forms. & 2 & Must \\ \hline
S1-US6 & UC14, UC15; HRUser.createJobPosting()/updateJobPosting(); JobRequirement.* & Create and update JobPosting with JobRequirement fields (required skills, nice-to-have, departments, minimum experience, notes). & 6 & Must \\ \hline
S1-US7 & UC16; HRUser.changeJobStatus(); JobPosting.openPosting()/closePosting() & JobPosting status transitions (draft, open, closed). & 3 & Must \\ \hline
S1-US8 & UC17; HRUser.deleteJobPosting() & Delete JobPosting and enforce integrity checks. & 3 & Should \\ \hline
\textbf{Total} &  & \textbf{Sprint 1 duration} & \textbf{28} &  \\ \hline
\end{longtable}
